Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-31 journal/article.tex
T: Communities

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.31\textwidth}
                     >{\raggedright\arraybackslash}p{0.61\textwidth} }
        Activity           &  Described in  \\
        \midrule
        Training    &
                P3, P6, P8, P9, P11, P16, P18-P21, P23-P25, P27, P30,
                P32, P35, P37, P39-P41, P43-P46, P48-P51  \\  % 29
        Coaching    &
                P1-P3, P6, P8, P9, P11, P16, P18, P23, P27, P29,
                P31-P33, P36, P39-P41, P45-P47, P49, P50, P52  \\  % 25
        In-house coaching   &
                P1-P3, P6, P11, P16, P23, P29, P31, P32,
                P39, P41, P45, P47, P49, P50, P52  \\    % 17
        Seminars and workshops   &
                P1-P4, P7, P9, P10, P11, P16, P23, P25,
                P26, P27, P32, P41, P44, P46, P47   \\   % 18
        \bottomrule
    \end{tabular}
    \caption{Summary of activities for building awareness and knowledgeability
             in the agile way of working}
    \label{table:transformation_training}
\end{table}

@@

% Content of events
In addition to general training and enabling awareness, the purpose of agile
events was to evangelize and expand the agile model throughout the organization
[P1, P10, P23, P32, P46].
Workshops were used to get people better involved [P16], and public lectures
were used to set straight sidetracks in the agile implementation[P26].
Hands-on workshops were used as a more engaging teaching method compared to
traditional lectures [P32, P41]. Open events were good for delivering the same
message to many people at the same time. As everyone could heard the same
questions and answers the understanding was consistent [P9, P41].
Workshops were arranged for identifying problems and planning the new model [P7,
P16, P27].

>>>>

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.31\textwidth}
                     >{\raggedright\arraybackslash}p{0.61\textwidth} }
        Activity           &  Described in  \\
        \midrule
        Training    &
                P3, P6, P8, P9, P11, P16, P18-P21, P23-P25, P27, P30,
                P32, P35, P37, P39-P41, P43-P46, P48-P51  \\  % 29
        Coaching    &
                P1-P3, P6, P8, P9, P11, P16, P18, P23, P27, P29,
                P31-P33, P36, P39-P41, P45-P47, P49, P50, P52  \\  % 25
        In-house coaching   &
                P1-P3, P6, P11, P16, P23, P29, P31, P32,
                P39, P41, P45, P47, P49, P50, P52  \\    % 17
        Seminars and workshops   &
                P1-P4, P7, P9, P10, P18, P11, P16, P23, P25,
                P26, P27, P32, P41, P44, P46, P47   \\   % 19
        Communities, special interest groups  &
                P3, P6, P7, P9, P10, P11, P12, P14, P32, P41,
                P42, P45, P47, P52  \\   % 14 
        \bottomrule
    \end{tabular}
    \caption{Summary of activities for building awareness and knowledgeability
             in the agile way of working}
    \label{table:transformation_training}
\end{table}

@@

% Content of events
In addition to general training and enabling awareness, the purpose of agile
events was to evangelize and expand the agile model throughout the organization
[P1, P10, P23, P32, P46].
Workshops were used to get people better involved [P16], and public lectures
were used to set straight sidetracks in the agile implementation [P26].
Hands-on workshops were used as a more engaging teaching method compared to
traditional lectures [P32, P41]. Open events were good for delivering the same
message to many people at the same time. As everyone could heard the same
questions and answers the understanding was consistent [P9, P41].
Workshops were arranged for identifying problems and planning the new model [P7,
P16, P27].

% SIGs, CoPs, and community

Events and coaching activity were coordinated forms of promoting the new model,
but the agile transformation gave also birth to communities [P3]. Typically
communities were emerging later in the transformation, when the rollout team
was starting to step aside [P3, P41].
In some cases the communities were created by passionate individuals without
corporate intervention, and participation in communities was voluntary [P47].
Communities were created when the mass of people involved became too large for
formal control [P52].
In other cases the forming of communities was stimulated by the organization
[P12, P45].
Companies strived to create communities of practice [P42] or special interest
groups [P41] in order to reinforce continuous learning in the organization.
Communities helped people to form a learning habit, which promoted continuous
improvement in the organization [P52].
